Eliminating object prior-bias from sparse-projection tomographic reconstructions

### 2021-10-07 paper/post_tci.tex
commented out the equation for RMSE, and changed the language a tad in the results section.

In this section, we first illustrate the advantage of using multiple
types of eigenspaces for the computation of weights map, and then
present reconstruction results on all datasets. For quantitative
evaluation, we use two metrics: the Root Mean Squared Error (RMSE) and the
Structural Similarity Index Metric (SSIM)~\cite{ssim}. If
$\boldsymbol{x}$ is the groundtruth data with $N$ voxels and
$\hat{\boldsymbol{x}}$ is the reconstructed data, then RMSE is
computed as follows

\begin{equation}
  \textrm{RMSE} =\sqrt{\frac{1}{N}\sum_{i=1}^N(\boldsymbol{x}(i) -
    \hat{\boldsymbol{x}}(i))^2}.
 \end{equation}

Since RMSE corresponds to error in intensity values, we have used SSIM
with a higher weightage to structure for the purpose of measuring
error in preservation of structures in our reconstructions. Hence, while
computing SSIM, we assign the following weights to structure, contrast
and intensity respectively: $0.7,0.2,0.1$.
%The reason for emphasizing the structure with an
%exponent of 0.7 stems from the optimization process since the
%intensity span (and, in general, the histogram) of reconstructed volumes
%differ across various methods and solvers.

>>>>

In this section, we first illustrate the advantage of using multiple
types of eigenspaces for the computation of weights map, and then
present reconstruction results on all datasets. We show both
qualitative and quantitative results. For the latter,
we use two metrics: the Root Mean Squared Error (RMSE) and the
Structural Similarity Index Metric (SSIM)~\cite{ssim}. 
% If
% $\boldsymbol{x}$ is the groundtruth data with $N$ voxels and
% $\hat{\boldsymbol{x}}$ is the reconstructed data, then RMSE is
% computed as follows

% \begin{equation}
%   \textrm{RMSE} =\sqrt{\frac{1}{N}\sum_{i=1}^N(\boldsymbol{x}(i) -
%     \hat{\boldsymbol{x}}(i))^2}.
%  \end{equation}
While RMSE corresponds to error in intensity values and is a measure
of absolute error, SSIM seeks to consider perceptual changes, as well
as correlation between adjacent pixels. This can be useful in a
clinical context.  We therefore assign a higher weightage to structure
preservation, that is we assign the
following weights to structure, contrast, and intensity respectively:
$0.7,0.2,0.1$.

It can be verified that in all cases, our results are favourable for the
various datasets considered.
%The reason for emphasizing the structure with an
%exponent of 0.7 stems from the optimization process since the
%intensity span (and, in general, the histogram) of reconstructed volumes
%differ across various methods and solvers.
